A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-16 paper.tex
Mention Tangle for the network of IOTA. Mention IOTA for the ecosystem

Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer. The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, which introduces properties like publishing, classifying and tracking authenticated message streams. It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible. 2) \textbf{Integrity}, messages written on the Tangle are immutable. 3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents. 4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents. See Fig.~\ref{fig:channel_and_key} for illustration.

@@

However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

@@

In our architecture, a decentralized identity system TangleID\cite{TangleID} is adopted, built on top of MAM where change logs of DIDs are traceable. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.

@@

\subsection{Delegate MAM operations to Accel}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

@@

\subsection{Gas usage of the Product Contract}
We investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix. On top of this evaluation, data providers can consider how to set the subscription and brokereage fee to eventually generate profits. The estimated cost is in USD, where $1\ Ether = 238\ USD$ at the time of writing, yet the price is dynamic from time to time. To conquer this condition, we analyze with a fixed range of Gas price. According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price. Note that data uploading is only related to MAM operations on IOTA, which does not require any fees. Therefore, the Gas estimation only includes trading processes. The high transaction fee for brokers are due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper. Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.

>>>>

Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token and applies MAM as the data storage and data transmission layer. The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams by implementing the second layer data communication protocol built on top of IOTA network, the Tangle, which has properties like publishing, classifying and tracking authenticated message streams. It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible. 2) \textbf{Integrity}, messages written on the Tangle are immutable. 3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents. 4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents. See Fig.~\ref{fig:channel_and_key} for illustration.

@@

However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM requires lots of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

@@

In our architecture, a decentralized identity system TangleID\cite{TangleID} is adopted, built on top of MAM where audit logs of DIDs are traceable. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, consisting of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the Tangle, represents the ownership of all things associated with the user in the IOTA ecosystem.

@@

\subsection{Delegate MAM operations to Accel}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources with, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

@@

\subsection{Gas usage of the Product Contract}
We investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix. On top of this evaluation, data providers can consider how to set the subscription and brokereage fee to eventually generate profits. The estimated cost is in USD, where $1\ Ether = 238\ USD$ at the time of writing, yet the price is dynamic from time to time. To conquer this condition, we analyze with a fixed range of Gas price. According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price. Note that data uploading is only related to MAM operations on the Tangle without transaction fee. Therefore, the Gas estimation only includes trading processes. The high transaction fee for brokers are due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper. Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
